The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-11-01 ApJ/ms.tex
Addressing two more points.

\begin{figure*}
\plottwo{f6a}{f6b}
\caption{\label{fig:pops} The scatter plots show the SF history of the
  quiet (left) and intense (right) halos as a function of metallicity
  at $z=7$.  Each circle represents a star cluster, whose area is
  proportional to its mass.  The open circles in the upper right
  represent $10^3$, $10^4$, and $10^5$ \Ms~star clusters.  The dashed
  lines in the right panel guide the eye to two stellar populations
  that were formed in two satellite halos, merging at $z=7.5$.  The
  upper histogram shows the SFR.  The right histogram depicts the
  stellar metallicity distribution.}
\end{figure*}

@@

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \citep{Wolfe05_Review, Penprase10}, and metal
enrichment from Pop III SNe provides a possible explanation
\citep{Kobayashi11}.  Ours is the first simulation with sufficient
physics and resolution to support this claim.

>>>>

\begin{figure*}
\plottwo{f6a}{f6b}
\caption{\label{fig:pops} The scatter plots show the metal-enriched
  (Pop II) star formation history of the intense (left) and quiet
  (right) halos as a function of total metallicity, i.e. the sum of
  metal ejecta from both Pop II and Pop III SNe, at $z=7$.  Each
  circle represents a star cluster, whose area is proportional to its
  mass.  The open circles in the upper right represent $10^3$ and
  $10^4$ \Ms~star clusters.  The upper histogram shows the SFR.  The
  right histogram depicts the stellar metallicity distribution.  The
  intense halo shows a large spread in metallicity at $z>10$ because
  these stars formed in progenitor halos that were enriched by
  different SN explosions.  At $z<10$, the majority of stellar
  metallicities increase as the halo is self-enriched.  The spikes in
  metallicity at $t$ = 620, 650, and 700 Myr show induced star
  formation with enhanced metallicities in SN remnant shells.  The
  dashed lines in the left panel guide the eye to two stellar
  populations that were formed in two satellite halos, merging at
  $z=7.5$.  The quiet halo evolves in relative isolation and steadily
  increases its metallicity to [Z/H] $\sim$ --2 until there is an
  equilibrium between \textit{in-situ} star formation and metal-poor
  inflows from filaments.}
\end{figure*}

@@

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \citep{Wolfe05_Review, Penprase10}, and metal
enrichment from Pop III SNe provides a possible explanation
\citep{Kobayashi11}.  Our simulation strengthens this claim of a
metallicity floor from Pop III SNe \citep[see also][]{Tornatore07,
  Karlsson08, Maio11_Enrich}, where our work improves on previous
studies by resolving star-forming molecular clouds and employing more
realistic feedback physics, in particular, radiation transport.
